---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
    theme: journal
    highlight: tango
    toc: true
    toc_float: true 
    css: styles.css
    code_folding: show
---

```{r loadlibs, echo=FALSE, results='hide', message=FALSE}
library(dplyr)
library(ggplot2)
```

```{r setoptions, echo=TRUE}

```

## Code for reading in the dataset and/or processing the data
```{r lpaddata, echo=TRUE}
activity_data <- read.csv('activity.csv', na.string='NA')
activity_data$date <- as.POSIXct(strptime(activity_data$date, '%Y-%m-%d'))
dim(activity_data)
# Remove all missing Values
activity_data <- activity_data[!is.na(activity_data$steps),]
# avgByDate <- aggregate(activity_data$steps, by=list(date=as.factor(activity_data$date)), mean)


```

## What is mean total number of steps taken per day?
### 1. Histogram of the total number of steps taken each day
```{r}
gStepsPerDay <- group_by(activity_data, date) %>% summarize(totalStepsPerDay=sum(steps))
qplot(gStepsPerDay$totalStepsPerDay, 
      geom = 'histogram', 
      binwidth=1000, 
      main = 'Total Steps taken each Day',
      xlab = 'Total Steps taken per day',
      ylab = 'Frequency',
      fill = I('blue'),
      col = I('red'))
```

### 2. Calculate and report the mean and median total number of steps taken per day
```{r}
gStepsPerDay <- activity_data %>% 
    group_by(date) %>% 
    summarize(meanStepsPerDay=mean(steps), medianStepsPerDay=median(steps, na.rm=TRUE))
print(gStepsPerDay)
```

## What is the average daily activity pattern?

### 1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
```


### 2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
